httping
=======

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

`httping` is a tiny R package to Ping urls to time requests. It's a port of the Ruby gem [httping](https://github.com/jpignata/httping).

## Philosophy

* The web is increasingly a JSON world, so we set `content-type` and `accept` headers to `applications/json` by default 
* The workflow follows logically, or at least should, from, _hey, I got this url_, to _i need to add some options_, to _execute request_
* Whenever possible, we transform output to data.frame's - facilitating downstream manipulation via `dplyr`, etc.
* We do `GET` requests by default. Specify a different type if you don't want `GET`
* You can use non-standard evaluation to easily pass in query parameters without worrying about `&`'s, URL escaping, etc. (see `query()`)
* Same for body params (see `body()`)

All of the default just mentioned can be changed. 

## Quick start

### Install

One non-CRAN dep (`httpcode`) needs to be installed first.

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("sckott/httpcode")
devtools::install_github("sckott/httping")
```

```{r}
library("httping")
```

## Pass any httr request to time

A `GET` request

```{r}
GET("http://google.com") %>% time(count=3)
```

A `POST` request

```{r}
POST("http://httpbin.org/post", body = "A simple text string") %>% time(count=3)
```

The return object is a list with slots for all the `httr` response objects, the times for each request, and the average times. The number of requests, and 
the delay between requests are included as attributes. 

```{r}
res <- GET("http://google.com") %>% time(count=3)
attributes(res)
```

Or print a summary of a response, gives more detail

```{r}
res %>% summary()
```

Messages are printed using `cat`, so you can suppress those using `verbose=FALSE`, like 

```{r}
GET("http://google.com") %>% time(count=3, verbose = FALSE)
```


## Ping an endpoint

This function is a bit different, accepts a url as first parameter, but can accept any args passed on to `httr` verb functions, like `GET`, `POST`,  etc. 

```{r}
"http://google.com" %>% ping()
```

Or pass in additional arguments to modify request

```{r}
"http://google.com" %>% ping(config=verbose())
```

## Even simpler verbs

Playing around with this idea. `httr` is already easy, but `Get()`:

* Allows use of an intuitive chaining workflow
* Parses data for you using `httr` built in format guesser, which should work in most cases

A simple GET request

```{r}
"http://httpbin.org/get" %>%
  Get()
```

You can buid up options by calling functions

```{r message=TRUE}
"http://httpbin.org/get" %>%
  Progress() %>%
  Verbose()
```

Then eventually execute the GET request

```{r message=TRUE}
"http://httpbin.org/get" %>%
  Progress() %>%
  Verbose() %>%
  Get()
```

## The new setup

Default 

```{r message=TRUE}
"http://api.crossref.org/works" %>%
  Get()
```

Use query parameters

```{r message=TRUE}
"http://api.plos.org/search" %>%
  query(q="*:*", wt="json", fl="id,journal,counter_total_all")
```

Use body parameters

```{r message=TRUE}
"http://httpbin.org/put" %>%
  body(x = "hello world!")
```
