httping
=======

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![cran checks](https://badges.cranchecks.info/worst/httping.svg)](https://cloud.r-project.org/web/checks/check_results_httping.html)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/httping?color=C9A115)](https://github.com/metacran/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/httping)](https://cran.r-project.org/package=httping)

`httping` is a tiny R package to Ping urls to time requests. It's a port of the Ruby gem [httping](https://github.com/jpignata/httping).

## Install

CRAN stable version

```{r eval=FALSE}
install.packages("httping")
```

Development version from Github

```{r eval=FALSE}
install.packages("pak")
pak::pkg_install("sckott/httping")
```

```{r}
library("httping")
library("httr")
```

## Pass any httr request to time

A `GET` request

```{r}
GET("https://google.com") %>% time(count = 3)
```

A `POST` request

```{r}
POST("https://mockbin.com/request", body = "A simple text string") %>% time(count = 3)
```

The return object is a list with slots for all the `httr` response objects, the times for each request, and the average times. The number of requests, and
the delay between requests are included as attributes.

```{r}
res <- GET("http://google.com") %>% time(count = 3)
attributes(res)
```

Or print a summary of a response, gives more detail

```{r}
res %>% summary()
```

Messages are printed using `cat`, so you can suppress those using `verbose=FALSE`, like

```{r}
GET("https://google.com") %>% time(count = 3, verbose = FALSE)
```


## Ping an endpoint

This function is a bit different, accepts a url as first parameter, but can accept any args passed on to `httr` verb functions, like `GET`, `POST`,  etc.

```{r}
"https://google.com" %>% ping()
```

Or pass in additional arguments to modify request

```{r}
"https://google.com" %>% ping(config = verbose())
```

## Meta

* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
