httping
=======

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

`httping` is a tiny R package to Ping urls to time requests. It's a port of the Ruby gem [httping](https://github.com/jpignata/httping).

## Quick start

### Install

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("sckott/httping")
```

```{r}
library("httping")
```

## Pass any httr request to time

A `GET` request

```{r}
GET("http://google.com") %>% time(count=3)
```

A `POST` request

```{r}
POST("http://httpbin.org/post", body = "A simple text string") %>% time(count=3)
```

The return object is a list with slots for all the `httr` response objects, the times for each request, and the average times. The number of requests, and 
the delay between requests are included as attributes. 

```{r}
res <- GET("http://google.com") %>% time(count=3)
attributes(res)
```

Or print a summary of a response, gives more detail

```{r}
res %>% summary()
```

Messages are printed using `cat`, so you can suppress those using `verbose=FALSE`, like 

```{r}
GET("http://google.com") %>% time(count=3, verbose = FALSE)
```


## Ping an endpoint

This function is a bit different, accepts a url as first parameter, but can accept any args passed on to `httr` verb functions, like `GET`, `POST`,  etc. 

```{r}
"http://google.com" %>% ping()
```

Or pass in additional arguments to modify request

```{r}
"http://google.com" %>% ping(config=verbose())
```
